02_limma_hyp

### 2019-03-19 scripts/02_limma_hyp.Rmd
rename to change order
add nesting to building contrast

---
title: "03_limma_hyp"
output: md_document
---

@@

plotMDS(parentalobject,col=col.treatment, labels = colData$sex)
legend("bottomright",fill=c("#a6cee3", "#1f78b4", "#b2df8a", "#33a02c", "#fb9a99", "#e31a1c", "#fdbf6f", "#ff7f00", "#cab2d6"),legend=levels(colData$treatment))
title("Hypothalamus Colored by Treatment")

@@

	         MH_CB = male.hypothalamus.control - male.hypothalamus.bldg,
	         MH_BL = male.hypothalamus.bldg - male.hypothalamus.lay,
	         MH_Li3 = male.hypothalamus.lay - male.hypothalamus.inc.d3,
	         MH_i39 = male.hypothalamus.inc.d3 - male.hypothalamus.inc.d9,
	         MH_i917 = male.hypothalamus.inc.d9 - male.hypothalamus.inc.d17,
	         MH_i17H = male.hypothalamus.inc.d17 - male.hypothalamus.hatch,
	         MH_H5 = male.hypothalamus.hatch -  male.hypothalamus.n5,
	         MH_n59 = male.hypothalamus.n5 - male.hypothalamus.n9,
	         MH_n9C = male.hypothalamus.n9 - male.hypothalamus.control,
levels=parentaldesign)

@@

>>>>

---
title: "02_limma_hyp"
output: md_document
---

@@

plotMDS(parentalobject,col=col.treatment, labels = colData$sex)
legend("bottomleft",fill=c("#a6cee3", "#1f78b4", "#b2df8a", "#33a02c", "#fb9a99", "#e31a1c", "#fdbf6f", "#ff7f00", "#cab2d6"),legend=levels(colData$treatment))
title("Hypothalamus Colored by Treatment")

@@

	         MH_CB = male.hypothalamus.control - male.hypothalamus.bldg,
	         MH_BL = male.hypothalamus.bldg - male.hypothalamus.lay,
	         MH_Li3 = male.hypothalamus.lay - male.hypothalamus.inc.d3,
	         MH_i39 = male.hypothalamus.inc.d3 - male.hypothalamus.inc.d9,
	         MH_i917 = male.hypothalamus.inc.d9 - male.hypothalamus.inc.d17,
	         MH_i17H = male.hypothalamus.inc.d17 - male.hypothalamus.hatch,
	         MH_H5 = male.hypothalamus.hatch -  male.hypothalamus.n5,
	         MH_n59 = male.hypothalamus.n5 - male.hypothalamus.n9,
	         MH_n9C = male.hypothalamus.n9 - male.hypothalamus.control,

	         FH_n9B = female.hypothalamus.n9 - female.hypothalamus.bldg,
	         MH_n9B = male.hypothalamus.n9 - male.hypothalamus.bldg,
levels=parentaldesign)

@@

## nesting to building

cont <- "FH_n9B"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='FH_n9B', frame.plot=F)

cont <- "MH_n9B"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='MH_n9B', frame.plot=F)
